\section{Work}
%
\cventry{2022}{Research Intern - Program Analysis}{SRI International}{Melno Park, CA}{}
{
    \begin{itemize}
        \item Developed a graph-based model of code evolution to identify code
              changes that introduce security vulnerabilities.
        \item Applied static analysis techniques to detect security
              vulnerabilities in software.
        \item Working with the Linux Foundation to integrate the approach into
              the Linux Kernel CI/CD pipeline.
        \item Used LLVM, Static Analysis, Neo4j, Mining Software Repositories.
    \end{itemize}
}

\cventry{2021}{Research Intern - Intelligent Systems Lab}{PARC, a Xerox Company}{Palo Alto, CA}{}
{
    \begin{itemize}
        \item Evaluated neural decompilation methods to locate and isolate
              software features in binary applications.
        \item Designed search-based techniques for software re-synthesis,
              enabling the automatic reconstruction of software applications
              from their binary code.
        \item Developed methods for evaluating the equivalency of software
              applications, which can be used to verify the correctness of
              software transformations and repairs.
        \item Used Ghidra, GDB, Python.
    \end{itemize}
}

% \cventry{Winter 2017}{Winter Intern - Web3}{MIT Media Lab, Human Dynamics
%     Group}{}{} {
%     \begin{itemize}
%         \item Mentored by \href{https://web.media.mit.edu/~dang/}{Dazza
%                   Greenwood}, a leading expert in Web3 and decentralized
%               identity.
%         \item Investigated and designed applications that use decentralized
%               identities to empower users and communities.
%         \item Prototyped a decentralized autonomous organization (DAO) to enable
%               collective decision-making and governance.
%         \item Used Node.js, Solidity, web3.js, Ethereum, and TravisCI to develop
%               and deploy Web3 applications.
%     \end{itemize}
% }

\cventry{2014 - 2017}{Software Developer/Founding
    Team}{\href{https://www.getsimpl.com/}{Simpl}}{Bangalore, India}{} {
    \begin{itemize}
        \item Developed and maintained a payment platform for online merchants
              used by over 5 million users.
        \item Scaled the service to handle 100 million requests a day using an
              event-based/pub-sub microservice.
        \item Built the data engineering pipeline to support BI queries.
        \item Used Golang, Ruby on Rails, Python, Redis, Kafka, RabbitMQ, Spark,
              Cassandra, and AWS.
    \end{itemize}
}
